Using VariantSpark to uncover the link between obesity and cancer

### 2015-10-07 doc/publications/Recomb15/recomb15.tex
grammar

We therefore utilise the {\sc Spark} engine in our recently developed framework, \variantSpark~\cite{OBrien}, for applying machine learning methods to standard variant files in Variant Call Format (VCF). 
Unlike {\sc Hadoop}, {\sc Spark} allows a more flexible software design to utilise node-parallelisation and offers in memory cashing, both critically components for efficient "big learning" tasks.

>>>>

We therefore utilise the {\sc Spark} engine in our recently developed framework, \variantSpark~\cite{OBrien}, for applying machine learning methods to standard variant files in Variant Call Format (VCF). 
Unlike {\sc Hadoop}, {\sc Spark} allows a more flexible software design to utilise node-parallelisation and offers in-memory cashing, both critical components for efficient "big learning" tasks.
